% Maximum information density, 10pt, tight everything, guaranteed 1 page
\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{fontawesome5}

\geometry{margin=0.4in, top=0.35in, bottom=0.35in}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\definecolor{accent}{HTML}{333333}
\definecolor{rule}{HTML}{AAAAAA}
\definecolor{RULE}{HTML}{AAAAAA}  % uppercase alias (titlesec/\uppercase can expand this)
\definecolor{light}{HTML}{666666}

\hypersetup{colorlinks=true, urlcolor=accent}

\titleformat{\section}{\normalsize\bfseries\color{accent}\uppercase}{}{0pt}{}[\vspace{0pt}{\color{rule}\hrule height 0.5pt}]
\titlespacing*{\section}{0pt}{6pt}{3pt}

\setlist{left=0pt, itemsep=0pt, topsep=1pt, partopsep=0pt, parsep=0pt}

\newcommand{\entry}[4]{%
  {\small\bfseries #1} \hfill {\footnotesize\color{light}#2} \\[-1pt]
  {\footnotesize\itshape #3 \hfill #4} \\[-4pt]
}

\begin{document}

% ---- HEADER ----
\begin{center}
  {\Large\bfseries Omar Hyjek} \\[2pt]
  {\footnotesize\color{light}
    \faIcon{map-marker-alt}\enspace Detroit, MI \enspace\textbar\enspace
    \faIcon{phone}\enspace 313\,491\,9726 \enspace\textbar\enspace
    \faIcon{envelope}\enspace \href{mailto:ohyjek@gmail.com}{ohyjek@gmail.com} \enspace\textbar\enspace
    \faLinkedin\enspace \href{https://www.linkedin.com/in/hyjeko}{linkedin.com/in/hyjeko} \enspace\textbar\enspace
    \faGithub\enspace \href{https://github.com/ohyjek}{github.com/ohyjek}
  }
\end{center}

\vspace{-4pt}

% ---- SUMMARY ----
\section*{Summary}
{\small Senior frontend engineer with 10+ years of professional experience building consumer-facing web applications at scale. Currently contributing to micro-frontend architecture at Care.com.}

% ---- SKILLS (up top for scannability) ----
\section*{Skills}
\vspace{-2pt}
\begin{multicols}{2}
{\footnotesize
\textbf{Frontend:} TypeScript, JavaScript, React/Preact, Next.js, SolidJS, Apollo Client, GraphQL, Redux, RTK Query, MUI, Emotion, Tailwind, Storybook

\textbf{Backend:} Node.js, Fastify, GraphQL, Docker, Kubernetes, PostgreSQL, nginx

\columnbreak

\textbf{Tools:} JIRA, Jenkins, pnpm, Turborepo, Vite, Webpack, LaunchDarkly, Sentry, Amplitude, Datadog, Figma, Cursor, Jest, Playwright, Corepack

\textbf{Architecture:} Micro-frontends, monorepos, feature flag development, test-driven development, legacy modernization
}
\end{multicols}

\vspace{-6pt}

% ---- EXPERIENCE ----
\section*{Experience}

\entry{Care.com}{May 2025 -- Present}{Senior Software Engineer}{United States}
\begin{itemize}[nosep]
  \item {\small Led a dependency audit and upgrade initiative across micro-frontends (developed and presented the plan to our organization), helping to address version drift and inconsistent dependency usage patterns.}
  \item {\small Dramatically improved Sentry quota usage rates by implementing custom client-side filtering for the onSend event in the Sentry SDK.}
  \item {\small Owned frontend implementation of the Seeker Hiring Hub feature; scoped the work alongside design, wrote the development plan and JIRA tickets. Implemented alongside another engineer.}
  \item {\small Regularly picked up iOS (Swift/SwiftUI) bug fixes outside core frontend responsibilities to unblock the mobile team.}
  \item {\small Reduced team bug count from 70+ to 0 in 6 months.}
  \item {\small Collaborated with product to understand and define Amplitude metrics and events for the Seeker Hiring Hub feature.}
  \item {\small Used feature flag-driven development with LaunchDarkly to enable safe rollouts and A/B experimentation at scale.}
  \item {\small Worked across 7+ Next.js/TypeScript/Apollo micro-frontends; built and maintained features across Care.com's consumer marketplace.}
  \item {\small Adapted to using new AI tooling like Cursor and Claude to improve my workflow and productivity. JIRA MCP is a game changer.}
\end{itemize}

\vspace{2pt}
\entry{RIIS LLC}{Mar 2024 -- Apr 2025}{Senior Software Engineer}{Detroit, MI}
\begin{itemize}[nosep]
  \item {\small Built the WebRTC video/audio feed for Flock Safety's drone dock UI; worked with the principal engineer on state management, picked mitt for pub/sub to handle high message throughput.}
  \item {\small AcreConnect: Enhanced API fetching layer with type parameters for more confident reasoning about data fetching interfaces.}
\end{itemize}

\vspace{2pt}
\entry{RIVET Work}{Mar 2023 -- Mar 2024}{Senior Software Engineer 4}{Detroit, MI}
\begin{itemize}[nosep]
  \item {\small Migrated legacy React codebase from Create React App to Vite; improved build times by 10$\times$.}
  \item {\small Implemented RTK Query in order to demonstrate separation of concerns between state management and data fetching.}
  \item {\small Advocated for modern package tooling like pnpm in order to improve build times and reduce bundle size.}
  \item {\small Regularly gave constructive feedback on code reviews and provided guidance on best practices for React and web development.}
\end{itemize}

\vspace{2pt}
\entry{Airspace Link, Inc.}{Aug 2022 -- Feb 2023}{Software Engineer}{Detroit, MI}
\begin{itemize}[nosep]
  \item {\small Contributed to the launch of Airhub Portal; built interactive map layers with Preact and ArcGIS for drone airspace management.}
\end{itemize}

\vspace{2pt}
\entry{Detroit Labs}{Mar 2016 -- Aug 2022}{Senior Software Developer}{Detroit, MI}
\begin{itemize}[nosep]
  \item {\small Helped ship over 5 client projects (Lineage, Rocket, Autospot, Driveway, and more).}
  \item {\small Led a frontend team on Autospot from initial scope to production. Involved in all aspects of frontend architecture and development.}
  \item {\small Often engaged with work outside of my core frontend responsibilities in order to broaden my skillset and help our team.}
  \item {\small Gave internal talks on React and web patterns like demystifying useEffect and useCallback, when to use React Context and when to use Redux, and what is transpiling for, anyway?}
  \item {\small Mentored junior developers by reviewing code and providing feedback and support on their projects.}
\end{itemize}

\vspace{2pt}
\entry{Compuware}{Feb 2015 -- Mar 2016}{Software Developer}{Detroit, MI}
\begin{itemize}[nosep]
  \item {\small Entry-level full-stack web application development.}
\end{itemize}

% ---- EDUCATION ----
\section*{Education}
{\small\textbf{Dickinson College} \hfill {\color{light}2010 -- 2014}} \\
{\small BS Computer Science \enspace\textbar\enspace BS Mathematics}

\end{document}
