% Maximum information density, 10pt, tight everything, guaranteed 1 page
\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{fontawesome5}

\geometry{margin=0.4in, top=0.3in, bottom=0.3in}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\definecolor{accent}{HTML}{333333}
\definecolor{rule}{HTML}{AAAAAA}
\definecolor{RULE}{HTML}{AAAAAA}  % uppercase alias (titlesec/\uppercase can expand this)
\definecolor{light}{HTML}{666666}

\hypersetup{colorlinks=true, urlcolor=accent}

\titleformat{\section}{\normalsize\bfseries\color{accent}\uppercase}{}{0pt}{}[\vspace{0pt}{\color{rule}\hrule height 0.5pt}]
\titlespacing*{\section}{0pt}{5pt}{2pt}

\setlist{left=0pt, itemsep=0pt, topsep=1pt, partopsep=0pt, parsep=0pt}

\newcommand{\entry}[4]{%
  {\small\bfseries #1} \hfill {\footnotesize\color{light}#2} \\[-1pt]
  {\footnotesize\itshape #3 \hfill #4} \\[-4pt]
}

\begin{document}

% ---- HEADER ----
\begin{center}
  {\Large\bfseries Omar Hyjek} \\[2pt]
  {\footnotesize\color{light}
    \faIcon{map-marker-alt}\enspace Detroit, MI \enspace\textbar\enspace
    \faIcon{phone}\enspace 313\,491\,9726 \enspace\textbar\enspace
    \faIcon{envelope}\enspace \href{mailto:ohyjek@gmail.com}{ohyjek@gmail.com} \enspace\textbar\enspace
    \faLinkedin\enspace \href{https://www.linkedin.com/in/hyjeko}{linkedin.com/in/hyjeko} \enspace\textbar\enspace
    \faGithub\enspace \href{https://github.com/ohyjek}{github.com/ohyjek}
  }
\end{center}

\vspace{-4pt}

% ---- SUMMARY ----
\section*{Summary}
{\small Full-stack engineer with 10+ years of experience shipping consumer-facing web applications end-to-end. Deep expertise in TypeScript, React, Next.js, GraphQL, and Node.js. Track record of owning products from scope to production in startup and early-stage environments. Currently writing internal guides and mentoring engineers on AI-augmented development workflows.}

% ---- SKILLS (up top for scannability) ----
\section*{Skills}
\vspace{-2pt}
\begin{multicols}{2}
{\footnotesize
\textbf{Full-stack:} TypeScript, React/Preact, Next.js, Node.js, Fastify, Apollo Client, GraphQL, PostgreSQL, Docker, Kubernetes

\textbf{Frontend:} SolidJS, Redux, RTK Query, Tailwind, Storybook, MUI, Emotion

\columnbreak

\textbf{Tools:} pnpm, Turborepo, Vite, Webpack, LaunchDarkly, Sentry, Amplitude, Datadog, Jest, Playwright, Figma

\textbf{Architecture:} Micro-frontends, monorepos, feature flags, real-time systems, test-driven development, legacy modernization
}
\end{multicols}

\vspace{-6pt}

% ---- EXPERIENCE ----
\section*{Experience}

\entry{Care.com}{May 2025 -- Present}{Senior Software Engineer}{United States}
\begin{itemize}[nosep]
  \item {\small Worked across 7+ Next.js/TypeScript/Apollo micro-frontends; shipped features end-to-end across Care.com's consumer marketplace.}
  \item {\small Owned the Seeker Hiring Hub feature from scope to delivery: collaborated with design and product, wrote the development plan, and implemented alongside another engineer.}
  \item {\small Led a dependency audit initiative across micro-frontends; developed and presented the technical plan to the broader engineering organization.}
  \item {\small Collaborated with product to define analytics strategy, implementing Amplitude metrics and events to measure feature impact.}
  \item {\small Reduced team bug count from 70+ to 0 in 6 months.}
  \item {\small Used feature flag-driven development with LaunchDarkly to enable safe rollouts and rapid experimentation at scale.}
  \item {\small Authored internal technical guides on AI-augmented development workflows; paired with engineers across the team to drive adoption of Cursor and AI tooling.}
  \item {\small Picked up iOS (Swift/SwiftUI) bug fixes outside core frontend responsibilities to unblock the mobile team.}
  \item {\small Improved Sentry quota usage by implementing custom client-side event filtering, reducing noise while preserving actionable error data.}
\end{itemize}

\vspace{2pt}
\entry{RIIS LLC}{Mar 2024 -- Apr 2025}{Senior Software Engineer}{Detroit, MI}
\begin{itemize}[nosep]
  \item {\small Built the real-time WebRTC video/audio feed for Flock Safety's drone dock UI; designed a pub/sub state management layer using mitt to handle high-frequency message throughput.}
  \item {\small Improved API data-fetching architecture with TypeScript generics for type-safe, composable data layer interfaces.}
\end{itemize}

\vspace{2pt}
\entry{RIVET Work}{Mar 2023 -- Mar 2024}{Senior Software Engineer 4}{Detroit, MI}
\begin{itemize}[nosep]
  \item {\small Migrated legacy React codebase from Create React App to Vite; improving build times by 10$\times$.}
  \item {\small Introduced RTK Query to separate data fetching from state management, improving codebase clarity and maintainability.}
  \item {\small Drove adoption of modern tooling (pnpm, updated build pipelines) to improve build performance and reduce bundle size.}
\end{itemize}

\vspace{2pt}
\entry{Airspace Link, Inc.}{Aug 2022 -- Feb 2023}{Software Engineer}{Detroit, MI}
\begin{itemize}[nosep]
  \item {\small Contributed to the launch of Airhub Portal; built interactive map layers with Preact and ArcGIS for drone airspace management.}
\end{itemize}

\vspace{2pt}
\entry{Detroit Labs}{Mar 2016 -- Aug 2022}{Senior Software Developer}{Detroit, MI}
\begin{itemize}[nosep]
  \item {\small Lead frontend engineer on Autospot (engineering team of 4); owned frontend architecture and technical decisions from initial scope through production.}
  \item {\small Shipped 5+ client products (Lineage, Rocket, Autospot, Driveway, and more), iterating rapidly based on client and user feedback.}
  \item {\small Mentored junior developers through code reviews and pairing; gave internal technical talks on React patterns and architecture.}
\end{itemize}

% ---- EDUCATION ----
\section*{Education}
{\small\textbf{Dickinson College} \hfill {\color{light}2010 -- 2014}} \\
{\small BS Computer Science \enspace\textbar\enspace BS Mathematics}

\end{document}
